\documentclass[a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{listings}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{lipsum}     % Can be removed after putting your text content
\usepackage{graphicx}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{siunitx}
\usepackage{amsmath}
\usepackage{physoly}
\pagestyle{fancy}
\numberwithin{equation}{section}
\titleformat{\section}
  {\large\scshape}{\thesection}{1em}{}
\titleformat{\subsection}
  {\normalfont\scshape}{\thesubsection}{1em}{}
\titleformat{\subsubsection}
  {\normalfont\scshape}{\thesubsubsection}{1em}{}
\pagenumbering{arabic}
\usepackage[
    backend=biber, 
    natbib=true,
    style=numeric,
    sorting=none
]{biblatex}
\usepackage{csquotes}
\addbibresource{citations.bib}

\setlength\parindent{0pt}

\title{\vspace{-50pt}\bfseries{\Large{Quirks of the Quantum Pendulum}}\vspace{-5pt}}
\author{\normalfont{Jonah Chen}\\\vspace{-3pt}\small{University of Toronto}\\
\vspace{-10pt}\small{\url{jonah.chen@mail.utoronto.ca}}}
\date{}

\begin{document}
\maketitle
\sffamily

Trying to make a three-blue-one-brown like video about the quantum harmonic oscillator, and many interesting properties that arise it if you just look slightly deeper than what is taught in a normal course.

\section{Introduction and Motivation}

\begin{script}
    What did you click on? We will talk about the quantum pendulum. I am a student and I have this taught to me multiple times. I hated how it was taught in class as it gave no insight whatsoever into the physics of the system, so in the spirit of three-blue-one-brown, I will teach a different way, a method usually taught in more advanced quantum mechanics courses, but hopefully digestable by a slightly above-average high school student. By the end of the video, I hope to explain how the pendulum actually oscillates, and how it is related to a completely different process involving the roulette wheel or radioactive materials, and also how we can saturate the heisenberg uncertainty principle to build lasers.
\end{script}

\begin{script}
    I decided to split the video into multiple segments. First, I will introduce the mathematical preliminaries since the maths required for our journey is quite complex. If you are strong at calculus and linear algebra, feel free to skip this section. Then, we will find the solutions to the quantum harmonic oscillator without having to solve the schrodinger's equation at all. Finally, from the insights we have gained, we will discuss uncover several interesting properties this system has and some of its applications to modern physics and engineering, which could seem opaque at the surface.
\end{script}

\subsection{Prereqs}
\begin{itemize}
    \item Basic calculus and linear algebra
\end{itemize}

\section{Mathematical Preliminaries}

\subsection{Linear Operators}

\subsection{Inner Product and Bra-Ket}

\input{math/hermitian.tex}
\input{math/schrodinger.tex}

\section{Solving the Quantum Pendulum}

We will try to solve for the energies and wavefunctions of the quantum harmonic oscillator. The hamiltonian is given by
\begin{align}
    \hat H&=\frac{\hat p^2}{2m}+\frac{1}{2}m\omega^2\hat x^2\label{qho_hamiltonian}
\end{align}

\input{sln/dimensionless.tex}
\input{sln/brute_force.tex}
\input{sln/operator.tex}

\section{Implications}

\subsection{Exponentials and Translations}

\subsection{Poisson Distribution and Coherent States}

\subsection{Uncertainty and Squeezed States}

\begin{thebibliography}{99}

\end{thebibliography}

\end{document}